Matching Bullets

### 2015-12-11 imaging-paper.Rnw
A little more about smoothing factors

\subsection{Varying smoothing factor}
As mentioned, the algorithm for peak/valley detection depends on the selection of a smoothing window, called the smoothing factor. In particular, for detecting and removing the grooves prior to fitting a Loess regression, we selected a smoothing factor of 35. We can investigate the performance of groove detection across different smoothing factors. Figure \ref{fig:varysmooth}...

>>>>

\subsection{Varying smoothing factor}
As mentioned, the algorithm for peak/valley detection depends on the selection of a smoothing window, called the smoothing factor. In particular, for detecting and removing the grooves prior to fitting a Loess regression, and for detecting the peaks/valleys of the loess residuals, we selected a smoothing factor of 35. We can investigate the performance of peak/valley detection across different smoothing factors. Figure \ref{fig:varysmooth} displays the resulting peaks and valleys across smoothing factors of 35, 5, and 65 respectively. It is immediately clear that a small smoothing factor like 5 is a poor choice. This results in a significant amount of noise in the data such that even just a point or two can skew the rolling average enough for a peak or valley to be detected. Given that the striation patterns are typically much larger, we're in effect muddying the waters by performing such minimal smoothing.

A larger smoothing factor on the other hand, like 65, seems to be a more plausible option. Most of the peaks/valleys present which are detected by a smoothing factor of 35 are also detected at 65. However, some notable issues arise. Notice that the peak on the left hand side of the image is smoothed out, and thus not detected. On the right hand side, the peak is just barely still present and hence detected. But in many cases, the large windows are smoothing out some of the structure that we wish to see. Furthermore, it can be seen that the peaks/valleys are often shifted relative to their position in the original loess residuals, or in the smoothed data with smaller smoothing factors.
